Binning Strategies and Related Loss for Large Data

### 2015-04-02 Paper.Rnw
Paragraph on the optimal alpha/2 offset proof in appendix

@@

%----------------------------------------------------------------------------
\subsection{Optimal Offset for Uniform Data Recorded to Resolution $\alpha$}\label{proof:offset}

>>>>

For data with a coarse resolution the location of the origin is also important because the origin controls the proximity of possible data values to bin centers. It can be shown analytically that for data with a resolution of $\alpha$ units that is spread symmetrically within bins, the origin that minimizes net spatial loss is located $\alpha/2$ units below the minimum values (see proof in Appendix~\ref{proof:offset}).

@@

%----------------------------------------------------------------------------
\subsection{Optimal Offset for Uniform Data Recorded to Resolution $\alpha$}
\label{proof:offset}
